Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-01-24 Ben_Manuscripts/stochastic_transport/cover_letter.tex
some tweaks to cover letter.
Cover letter updates with referees

	%\noindent May 3\textsuperscript{rd}, 2019\\
	\noindent \date

	\noindent Dear Editors,\\

@@

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and Michael R.
	Shirts, for	consideration for publication as a Research Article in Physical 
	Review E. We expect this work to be of significant interest to researchers 
	who study complex dynamics in both structured and amorphous soft materials.

	In this article, we use solute trajectories generated from 5$\mu$s molecular
	dynamics (MD) simulations of an inverted hexagonal (H\textsubsript{II}) phase
	self-assembled lyotropic liquid crystal (LLC) polymer membrane in order to 
	parameterize two different stochastic time series models capable of predicting
	solute flux and selectivity on a macroscopic scale. Realizations of both models
	quantitatively reproduce the mean squared displacements (MSDs) exhibited by 
	solutes in MD simulations. This is among the first studies to apply time 
	series modeling approaches in order to predict bulk materials properties.

	Recently, we characterized transport mechanisms exhibited by a series of 
	small polar solutes in an LLC Membrane (Coscia and Shirts \textit{J. Phys.
	Chem. B}, 123, 6314--6330 (2019)). We observed subdiffusive solute transport
	characterized by intermittent hops separated by periods of entrapment. In
	this work, we build on the chemical intuition gained from our previous study
	in order to formulate stochastic models which produce trajectory realizations
	that share the same dynamical properties as those exhibited by solutes in 
	our MD simulations. We explore two modeling approaches. First, based on the
	anomalous diffusion literature, we hypothesize that solutes are subject 
	to subordinated fractional Brownian or L\'evy motion. This implies that 
	solutes experience a series of dwell times separated by anti-correlated hop
	lengths. Our second approach adds state-dependent dynamics to standard Markov
	state modeling approaches. We model solute motion as a series of transitions
	between various trapped states, each with different dynamical properties.

%        Recently, we characterized an atomistic molecular model of an
%        LLC membrane that is maximally consistent with experimental
%        observations (Coscia et al. \textit{J. Phys. Chem. B}, 123,
%        289--309 (2019)). In this work, we observe and quantify
%        transport of water, sodium and 20 small polar solutes within
%        the pores of our atomistic H\textsubscript{II} phase LLC
%        membrane model. In general, all solutes exhibit subdiffusive
%        transport behavior characterized by intermittent hops between
%        long periods of entrapment. However, due the pores'
%        inhomogeneous architecture, we observed 3 different mechanisms
%        of entrapment. First, solutes can diffuse out of the pores and
%        become entangled between tails. Second, many of the solutes
%        are capable of donating hydrogen bonds to monomer head groups
%        for extended periods of time. Finally, solutes can associate
%        with monomer head group counter-ions within nanopores. Each
%        solute is influenced by each mechanism to varying degrees
%        dependent on its size and chemical functionality. We begin our
%        discussion with a broad description of these mechanisms in the
%        context of all solutes before restricting the discussion to
%        more detailed analyses of subsets of chemically-similar
%        solutes.

@@

		\item Menachem Elimelech is a leader in the development of membrane technologies
		for	water desalination and water reuse (Yale University, 203-432-2789,
		\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).

		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
		and various	nanostructured materials (Northeastern University, 617-373-8619 	
		\href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})

		\item Mahesh Mahanthappa has experience modeling soft materials using molecular dynamics
		including work on ion transport in various ordered liquid crystalline phases. 
		(University of Minnesota, 612-625-4599,\href{mailto:maheshkm@umn.edu}{maheshkm@umn.edu})

>>>>

	\noindent January 27\textsuperscript{th}, 2020\\
	%\noindent \date

	\noindent Dear Editors, \\

@@

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and
	Michael R.  Shirts, for consideration for publication as a Research
	Article in Physical Review E. We expect this work to be of significant
	interest to researchers who study complex dynamics in both structured
	and amorphous soft materials. \\

	In this article, we use 5$\mu$s molecular dynamics (MD) simulations of
	solutes moving through the pores of an inverted hexagonal phase
	lyotropic liquid crystal (LLC) polymer membrane in order to
	parameterize two different stochastic time series models capable of
	predicting solute flux and selectivity on a macroscopic scale.
	Realizations of both models quantitatively reproduce the mean squared
	displacements (MSDs) exhibited by the solutes in our MD simulations. We then
	demonstrate how we can use realizations orders of magnitude longer than
	our MD simulations in order to predict solute flux and selectivity.
	This is among the first studies to apply time series modeling
	approaches in order to predict bulk materials properties. \\

	Based the chemical intuition gained from our previous studies, we
	formulate the stochastic models so that they share the same dynamical
	properties as those exhibited by solutes in our MD simulations. 
	Recently, we characterized transport mechanisms exhibited by a series
	of small polar solutes in an LLC Membrane (Coscia and Shirts \textit{J.
	Phys. Chem. B}, 123, 6314--6330 (2019)). We observed subdiffusive
	solute transport characterized by intermittent hops separated by
	periods of entrapment. 
	%In this work, we build on the chemical intuition
	%gained from our previous study in order to formulate stochastic models
	%which produce trajectory realizations that share the same dynamical
	%properties as those exhibited by solutes in our MD simulations. 
	In this work, we explore two approaches for modeling this behavior.
	First, based on the anomalous diffusion literature, we hypothesize that
	solutes are subject to either subordinated fractional Brownian or
	L\'evy motion. This implies that solutes experience a series of dwell
	times separated by anti-correlated hop lengths. Our second approach
	adds state-dependent dynamics to standard Markov state modeling
	approaches. We model solute motion as a series of transitions between
	various trapped states, each with different dynamical properties. \\

@@

		\item Ralf Metzler is an expert in anomalous diffusion theory
			with applications to soft materials. (University of
			Potsdam, \href{mailto:kakania@uni-potsdam.de}{kakania @
			uni-potsdam.de})

		\item Aziz Ghoufi has studied molecular mechanisms of
			subdiffusive solute transport in nanostructured
			materials. (Institut de Physique de Rennes,
			\href:{mailto:aziz.ghoufi@univ-rennes1.fr}{aziz.ghoufi@univ-rennes1.fr})

		%BJC: elimelech is more experiment-focused
		%\item Menachem Elimelech is a leader in the development of
		%	membrane technologies for water desalination and water
		%	reuse (Yale University, 203-432-2789,
		%	\href{mailto:menachem.elimelech@yale.edu}{menachem.elimelech@yale.edu}).

		\item Richard Lueptow uses molecular simulations to understand
			transport processes in polymeric nanofiltration and
			reverse osmosis membranes. (Northwestern University
			\href{mailto:r-lueptow@northwestern.edu}{r-lueptow@northwestern.edu})

		%BJC: I don't think Paddison is as strong as the others
